\documentclass[a4paper, oneside, 12pt]{article}

\usepackage[english]{babel}
% \usepackage{mathpazo}
% \usepackage{anyfontsize}
% \usepackage{extsizes}
\usepackage{wasysym}
\usepackage{fontawesome5}
\usepackage[colorlinks = true , urlcolor = black]{hyperref}
\usepackage{setspace}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage[a4paper, top = 2.5cm, bottom = 2.5cm, outer = 2.5cm, inner = 2.5cm]{geometry}
\makeatletter
  \def\vhrulefill#1{\leavevmode\leaders\hrule\@height#1\hfill \kern\z@}
\makeatother


\begin{document}
\pagestyle{empty}

\begin{center} 
    \fontsize{10pt}{20pt}\selectfont
    \rmfamily{\Huge{\textbf{Rounak Das}}} \\
    \color{blue}{Computer Science UnderGrad} \\ 
    \color{black}
    \begin{tabular}{c | c | c}
        \phone{+91 8420865007} & \faGithub{\href{https://github.com/Rounak-Das-02}{\hspace{1mm}Rounak-Das-02}} & \faEnvelope{\hspace{1mm}dasrounak2002@gmail.com}
    \end{tabular}
\end{center}

\vspace{0.5mm}

\begin{flushleft}

  \color[HTML]{0F00FF}{\LARGE{Education}}  \color{gray}{\vhrulefill{1.5pt}}
  
  \vspace{2mm}
  \color{black}
  \textbf{Mahindra University} \textit{\hfill Hyderabad, India} 

  (Mahindra École Centrale) \textit{\hfill 2020-Present}
    \begin{itemize}[label = ]
      \item Bachelor of Technology in Computer Science, GPA: 8.9/10
    \end{itemize}
  
  \textbf{St.Augustine's Day School}  \textit{\hfill 2018-2020}
    \begin{itemize}[label = ]
      \item Indian School Certificate (XII-2020), 97.5\%
      \item Indian Certificate for Secondary Education (X-2018), 95.4\%
    \end{itemize}

\end{flushleft}

\begin{flushleft}

  \color[HTML]{0F00FF}{\LARGE{Skills}}  \color{gray}{\vhrulefill{1.5pt}}
  
  \vspace{2mm}
  \color{black}
  \textbf{Languages }: 
    \begin{itemize}[label =]
      \item C, C++, Python, Java, typescript/javascript 
    \end{itemize}
  \textbf{Platforms and Tools }: 
    \begin{itemize}[label =]
      \item MERN Stack, ROS2, Flask, Git, Linux
    \end{itemize}

\end{flushleft}


\begin{flushleft}

  \color[HTML]{0F00FF}{\LARGE{Projects}}  \color{gray}{\vhrulefill{1.5pt}}
  
  \vspace{2mm}
  \color{black}
  \textbf{Penholics }: 
    \begin{itemize}[label =]
      \item A ReactJS website for a facebook page meant to provide a platform for budding writers to showcase their talents
    \end{itemize}
  \textbf{Laser Weeding (Ongoing Project) }: 
    \begin{itemize}[label =]
      \item A high-powered laser based targetting system to kill weeds from a moving robot. Involves controlling of Pan and Tilt mechanisms of Gimbals and servo motors based on ROS2 
    \end{itemize}

  \textbf{Weather App }: 
    \begin{itemize}[label =]
      \item A Stylish and Classy Looking Weather App based on the latest MVVM architecture as recommended by Google Android Developers.
    \end{itemize}
  
  \textbf{Hawkeye }: 
    \begin{itemize}[label =]
      \item The Moderation bot of discord for Enigma - The computer Science Club Of Mahindra University
    \end{itemize}
  
  \textbf{Automated Github Bot }: 
    \begin{itemize}[label =]
      \item Implemented a Bot for identifying commits made using Github Webapp and also auto-rejecting the same. The bot is capable of closing Pull request and giving reasons for the same, as well as notify members of the organisation about any recent push or Pull request by means of Webhooks
    \end{itemize}
\end{flushleft}

\pagebreak



\begin{flushleft}
\color[HTML]{0F00FF}{\LARGE{Interests and Hobbies}}  \color{gray}{\vhrulefill{1.5pt}}
\vspace{2mm}

\color{black}

I used to play under Cricket Association of Bengal.

Being a hodophile, I also like talking to new people and understand their land and culture.
Apart from that, I love wildlife Photography as well as enjoy playing the Keyboard (Musical Synthesizer).

\end{flushleft}


\begin{flushleft}
  \color[HTML]{0F00FF}{\LARGE{Communication}}  \color{gray}{\vhrulefill{1.5pt}}
  \vspace{2mm}

  \color{black}
  \fontsize{12pt}{20pt}\selectfont
  \textbf{English:} Professional Working Proficiency

  \textbf{Bengali:} Native

  \textbf{Hindi:} Bilingual Proficiency

  \textbf{French:} Junior Secondary School

\end{flushleft}


\begin{flushleft}

  \color[HTML]{0F00FF}{\LARGE{Awards and Achievements}}  \color{gray}{\vhrulefill{1.5pt}}
  
  \vspace{2mm}
  
  \color{black}
  \textbf{Ideathon }: 
    \begin{itemize}[label =]
      \item Winner of Ideathon-2020 themed AI for Art, sponsored by Microsoft. Received reward of 1.25 Lakhs INR, presented by Dr. Rohini Srivastava (National Technology Officer) - Microsoft India
    \end{itemize}

  \textbf{Savishkar}: 
    \begin{itemize}[label =]
      \item Winner of Coding Competition in Savishkar Fest organised by Douglas Memorial Higher Secondary School
      \item Received honor and memento for being the Student Representative of my School
    \end{itemize}

  \textbf{Scholarships }: 
    \begin{itemize}[label =]
      \item Received Scholarship from CISCE in Class XII for being one of the top 1\% in ISC Examinations 2020.
      \item Received Scholarship from School for performance in ISC and ICSE examinations.
      \item Received Scholarship in 2nd Year of College worth of INR 1 Lakh.
    \end{itemize}
  
\end{flushleft}

\end{document}